% -*- root: ../ProjectPlan.tex -*-
\section{Cost management and resource assignment}

\subsection{Personnel costs}

We consider the following salaries for the required positions for the project:

\begin{itemize}
\item Systems Analyst: 400 \euro / day.
\item Senior Designer: 350 \euro / day.
\item Junior Designer: 200 \euro / day.
\item Systems Technician: 300 \euro / day.
\end{itemize}

These values will be used as the fixed cost for personnel throughout this document estimations, even if they come from SOTFCOM or UAMSOFT.

\subsection{Hardware costs}

For the project, three workstations must be acquired for development (1.650 \euro per unit) and another one for performance testing (3.200 \euro). Total hardware cost is then 8.150 \euro.

Additionally, the maintenance cost for current hardware and software is 1.050 \euro per month.

\subsection{Software costs}

A new integrated development environment will also be acquired, at a cost of 1.100 \euro per workstation. This environment includes all necessary software for the lifecycle of the project.

\subsection{Cost estimation}

Given the schedule detailed in the previous section (\ref{secTimeEstimation}), we present the resource assignment table with the corresponding costs for the whole project in table \ref{tblCostResourceEstimate}. As we can see, the total amount of worked hours is 10\% less than in the previous project plan but the budget is not exactly the 10\% less because of the hardware and workstations needed.

\begin{table}[hbtp]
\centering
\input{tex/ResourceCostEstimation.tex}
\caption{Cost estimation given the schedule}
\label{tblCostResourceEstimate}
\end{table}
